Global Distribution of Unintended Pregnancies and Contraceptive Usage

### 2024-04-05 products/manuscript/Manuscript.qmd
Updated our references section.

A full model incorporating five predictors (total SARC users, region, marital status, and maternal mortality rates due to unintended pregnancy and abortion) was built. Despite performing the best among the evaluated models and being validated through cross-validation, the full model exhibited tendencies towards overfitting the data.

@@

_Include citations in your Rmd file using bibtex, the list of references will automatically be placed at the end_

This paper [@leek2015] discusses types of analyses.

These papers [@mckay2020; @mckay2020a] are good examples of papers published using a fully reproducible setup similar to the one shown in this template.

Note that this cited reference will show up at the end of the document, the reference formatting is determined by the CSL file specified in the YAML header. Many more style files for almost any journal [are available](https://www.zotero.org/styles). You also specify the location of your bibtex reference file in the YAML. You can call your reference file anything you like, I just used the generic word `references.bib` but giving it a more descriptive name is probably better.

@@

# References

- https://pubmed.ncbi.nlm.nih.gov/32981858/
- https://www.sciencedirect.com/science/article/pii/S001078241730478X 
- https://www.sciencedirect.com/science/article/abs/pii/S0020729211005406 #legal status article
- https://www.guttmacher.org/report/adding-it-up-investing-in-sexual-reproductive-health-2019-methodology (Guttmacher source)
- https://pubmed.ncbi.nlm.nih.gov/35332057/ (original source of data)

>>>>

A full model incorporating five predictors (total SARC users, region, marital status, and maternal mortality rates due to unintended pregnancy and abortion) was built. Despite performing the best among the evaluated models and being validated through cross-validation and bootstrap method, the full model exhibited tendencies towards overfitting the data.

@@

@@

# References
_Include citations in your Rmd file using bibtex, the list of references will automatically be placed at the end_

[@heviaLegalStatusEmergency2012], [@jonathanmarcbearakCountryspecificEstimatesUnintended2022], [@kavanaughContraceptiveMethodUse2018], [@rivetContraceptionUseAttitudes2021]
